Enrich the datasets with new columns.

### 2020-08-26 inst/analysis/enrich_dataset.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center",
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

@@

```{r add_source}
eval_calls <- eval_calls %>% add_eval_source() %>% add_eval_source_type()
```

@@

```{r ast_size}
eval_calls <- eval_calls %>% add_ast_size()
```

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

now <- Sys.time()

@@

```{r add_source}
eval_calls <- eval_calls %>% add_eval_source(eval_calls_raw) %>% add_eval_source_type()
```

@@

```{r ast_size}
#eval_calls <- eval_calls %>% add_ast_size()
```

@@

There are `r nrow(eval_calls)` unique rows.

@@

The core dataset has `r nrow(eval_calls_core)` unique calls, the packages dataset, `r nrow(eval_calls_packages)` and the kaggle one, `r nrow(eval_calls_kaggle)`.

@@

Notebook execution was `r difftime(Sys.time(), now)`.
